
---
output:
  word_document: default
  html_document: default
---


---
title: "The willingness to Pay for Locally Produced Food among Norwegians"
author: "Learning Team 1"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
editor_options: 
  chunk_output_type: console
---

```{r global-options, include=TRUE, results=TRUE, cache =TRUE}
library(knitr)
knitr::opts_chunk$set(cache = TRUE, warning = FALSE,
                      message = FALSE, echo = TRUE,
                      dpi = 180, fig.width = 8, fig.width = 5)
library(tidyverse)
library(ggplot2)
library(sandwich)
library(stargazer)
library(GGally)
library(lme4)
library(MASS)

```

Lets build a model using the Norsk Monitoring Data to look into willingness to pay for locally produced food among Norwegian population. 

##set working directory
```{r}
setwd("C:/Users/santosh.kunwar01/Documents/R/EUR/MOA107")
gc()
rm(list = ls(all.names = TRUE))
```
##import data

```{r, results=FALSE}
library(haven)
NMDD <- haven::read_sav("Norsk_Monitor_Total_1985-2019_SPSS_31mars.sav")

```

##explore data
```{r, results=FALSE}
NMDD
```


##coerce survey Year as Date class

```{r}
##NMDD$s_year <- as.Date(NMDD$Year, format = "%Y")

```

##Check class of s_year

```{r}
#class(NMDD$s_year)

```

##check if respondent are repeated over the years

```{r, results=FALSE}
n_occur <- data.frame(table(NMDD$rspnr))

n_occur[n_occur$Freq > 1,]

```

##create new table by comprising only the years where the question
Willingness to pay more for local food was introduced (2013 on wards
in this case) and subset with variables of interest]

```{r, message=FALSE, warning=FALSE}
library(tidyverse)

NMD <- subset(NMDD, Year >= "2013",
              select = c(
                rspnr,
                Year,
                Kjonn,
                Alder,
                V34,
                Q227_5,
                Q227_6,
                Q244,
                Q245_1,
                Q245_2,
                Q245_3,
                Q245_4,
                Q245_5,
                Q245_6,
                Q245_7,
                Q251_24,
                Q258_5,
                Q269_17))
```

##check NMD

```{r}
NMD
```


##check if respondent were repeated
```{r, results = FALSE}
noccur <- data.frame(table(NMD$rspnr))
noccur[noccur$Freq > 1,]

```

#rename variable labels of variables of interest for convenient reading

```{r}
NMD <- rename(NMD, 
       gender= Kjonn,
       age= Alder ,
       edu_level= V34,
       pay_more= Q227_5 ,
       env_con_food= Q227_6 ,
       buy_often= Q244 ,
       place_regular_grocery= Q245_1 ,
       place_farmers_market= Q245_2,
       place_farm_shop= Q245_3,
       place_special_store= Q245_4 ,
       place_food_festival= Q245_5,
       place_elsewhere= Q245_6,
       not_purchased= Q245_7,
       freq_ost= Q251_24 ,
       freq_beer= Q258_5 ,
       good_selection_avail = Q269_17 )

```

##Check for renaming of variables

```{r}
NMD
```
##know value labels and change spss "labelling" to haven labelled, recode variables as necessary

```{r, results= FALSE}
#load expss
library(expss)
```

```{r}
expss::val_lab(NMD$gender) #level2, 1 = Mann, 2 = Kvinne

```
#Recode Value levels, and variable labels

#recode value levels (Kvinnne = 1, and Mann = 0)

```{r}
NMD$gender_factor <- with(NMD, 
                          if_else(gender == 1, 0,
                               if_else(gender == 2, 1,
                                       as.numeric(gender)        
                                               )))


NMD$gender_factor <- (labelled(NMD$gender_factor,
                                 c("Female" =1,
                                   "Male" = 0),
                                 label = "gender"
                               ))


expss::val_lab(NMD$gender_factor)
```


##check edu_level 
```{r}
expss::val_lab(NMD$edu_level)#level 5, 1=8 years school, 5 = Masters
```

##recode value levels of variable edu_level
```{r}
NMD$edu_level_factor <- labelled(NMD$edu_level,
                                 c("Inntil 8 years school" =1,
                                   "9-10 years school" =2,
                                   "11-13 years school" = 3,
                                   "Bachelors" = 4,
                                   "Masters" = 5),
                                 label = "Education Level")


expss::val_lab(NMD$edu_level_factor)
  
```

##check value levels for pay_more
```{r}

expss::val_lab(NMD$pay_more) #levels 4, 1=Strongly Agree
```

#recode value levels (Strongly Disagree = 1, and Strongly Agree = 4)

```{r}
NMD$pay_more_factor <- with(NMD, if_else(pay_more ==1, 4,
                              if_else(pay_more == 2, 3,
                                if_else(pay_more == 3, 2,
                                  if_else(pay_more == 4,1,
                                    as.numeric(pay_more)        
                              )))))


NMD$pay_more_factor <- (labelled(NMD$pay_more_factor,
                                 c("Strongly Disagree" =1,
                                   "Partially Disagree" = 2,
                                   "Partially Agree" =3,
                                   "Strongly Agree" = 4),
                                 label = "Willing to Pay More"
))

expss::val_lab(NMD$pay_more_factor)
```


##check value levels env_con_food
```{r}
expss::val_lab(NMD$env_con_food) #levels 4, 1=Strongly Agree

```
##Recode value levels (Strongly Disagree = 1, and Strongly Agree = 4)

```{r}
NMD$env_con_food_factor <- with(NMD,
                if_else(env_con_food ==1, 4,
                             if_else(env_con_food == 2, 3,
                                     if_else(env_con_food == 3, 2,
                                             if_else(env_con_food == 4,1,
                                                     as.numeric(pay_more)        
                                             )))))


NMD$env_con_food_factor <- (labelled(NMD$env_con_food_factor,
                                 c("Strongly Disagree" =1,
                                   "Partially Disagree" = 2,
                                   "Partially Agree" =3,
                                   "Strongly Agree" = 4),
                           label = "Environmentally Conscious Food Purchase"
                            ))

expss::val_lab(NMD$env_con_food_factor)

```

## check value levels

```{r}
expss::val_lab(NMD$Year)

#####
expss::val_lab(NMD$buy_often) #l 6 week/month/year/rarely/never/dont know
```

##recode  Weekly or more often =5, Never = 1

```{r}

NMD$buy_often_factor <- with(NMD,
                         if_else(buy_often == 5,1,
                                 if_else(buy_often == 4, 2,
                                     if_else(buy_often == 3, 3,
                                        if_else(buy_often == 2,4,
                                         if_else(buy_often ==1, 5,
                                           if_else(buy_often == 6, 6,
                                                   as.numeric(buy_often)
                                           
                                              )))))))


NMD$buy_often_factor <- (labelled(NMD$buy_often,
                             c("Weekly or more often" = 5,
                               "Monthly" = 4,
                               "Sometimes a year" = 3,
                               "Rarely" = 2,
                               "Never" = 1,
                               "Do not know"= 6),
                             label = "Frequency of Local Food Purchase"
                              ))
expss::val_lab(NMD$buy_often_factor)

```

##recode value levels

```{r}
expss::val_lab(NMD$place_regular_grocery)# dummy 1

NMD$place_grocery_factor <- (labelled(NMD$place_regular_grocery,
                                      c("Yes" = 1,
                                        "No" = 0),
                                      label = "Purchase in Regular Grocery"
))

expss::val_lab(NMD$place_grocery_factor)

```

##check and recode variable place_farmers_market

```{r}
expss::val_lab(NMD$place_farmers_market) #dummy 1

NMD$place_farmer_market_factor <- (labelled(NMD$place_farmers_market,
                                            c("Yes" = 1,
                                              "No" = 0),
                                            label = "Purchase in Farmer Market"
))

expss::val_lab(NMD$place_farmer_market_factor)

```

##check and recode variable place_farm_shop

```{r}
expss::val_lab(NMD$place_farm_shop) #dummy 1


NMD$place_farm_shop_factor <- (labelled(NMD$place_farm_shop,
                                        c("Yes" = 1,
                                          "No" = 0),
                                        label = "Purchase in Farm Shop"
))

expss::val_lab(NMD$place_farm_shop_factor)

```

## check and recode variable

```{r}
expss::val_lab(NMD$place_special_store)#dummy 1


```


##check and recode variable place_special_store

```{r}
NMD$place_special_store_factor <- (labelled(NMD$place_special_store,
                                            c("Yes" = 1,
                                              "No" = 0),
                                            label = "Purchase in Special Store"
))

expss::val_lab(NMD$place_special_store_factor)
```

## check and recode variable place_food_festival

```{r}
expss::val_lab(NMD$place_food_festival) #purchased at food festival dum 1

NMD$place_festival_factor <- (labelled(NMD$place_food_festival,
                                       c("Yes" = 1,
                                         "No" = 0),
                                       label = "Purchase at Food Festival"
))

expss::val_lab(NMD$place_festival_factor)
```

##check and recode variable place_elsewhere

```{r}
expss::val_lab(NMD$place_elsewhere) #purchased elsewhere dummy 1

NMD$place_elsewhere_factor <- (labelled(
  NMD$place_elsewhere,
  c("Yes" = 1,
    "No" = 0),
  label = "Purchased elsewhere"
))

expss::val_lab(NMD$place_elsewhere_factor)
```

##check and recode variable not_purchased

```{r}
expss::val_lab(NMD$not_purchased) #not purchased since 12 months dummy 1

NMD$not_purchased_factor <- (labelled(
  NMD$not_purchased,
  c("not_purchased_within_12_monthsr" = 1,
    "purchased_within_12_month" = 0),
  label = "Not Purchased since 12 months"
))
expss::val_lab(NMD$not_purchased_factor)
```

##check and recode variable freq_ost

```{r}
expss::val_lab(NMD$freq_ost) #8 levels


NMD$freq_ost_factor <- with(NMD,
                            if_else(freq_ost == 8,1,
                              if_else(freq_ost == 7,2,
                                if_else(freq_ost == 6,3,
                                  if_else(freq_ost == 5,4,
                                    if_else(freq_ost == 4,5,
                                      if_else(freq_ost == 3,6,
                                        if_else(freq_ost == 2,7,
                                          if_else(freq_ost == 1,8,
                                            as.numeric(freq_ost)
                                            )))))))))


NMD$freq_ost_factor <- (labelled(NMD$freq_ost_factor,
                           c("Never" = 1,
                             "Rarely" = 2,
                             "3-11 Times/Year" = 3,
                             "Once a Month" = 4,
                             "2-3 Times a Month" = 5,
                             "1-2 Times a Week" = 6,
                             "3-5 Times a Week" = 7,
                             "Daily" = 8),
                             label = "Frequency of Local Ost Consumption"))


expss::val_lab(NMD$freq_ost_factor)

```

## check and recode value levels

```{r}
expss::val_lab(NMD$freq_beer) #8 levels


NMD$freq_beer_factor <- with(NMD,
                            if_else(freq_beer == 8,1,
                              if_else(freq_beer == 7,2,
                                if_else(freq_beer == 6,3,
                                  if_else(freq_beer == 5,4,
                                    if_else(freq_beer == 4,5,
                                      if_else(freq_beer == 3,6,
                                        if_else(freq_beer == 2,7,
                                          if_else(freq_beer == 1,8,
                                          as.numeric(freq_beer)
                                  )))))))))

NMD$freq_beer_factor <- (labelled(NMD$freq_beer_factor,
                                 c("Never" = 1,
                                   "Rarely" = 2,
                                   "3-11 Times/Year" = 3,
                                   "Once a Month" = 4,
                                   "2-3 Times a Month" = 5,
                                   "1-2 Times a Week" = 6,
                                   "3-5 Times a Week" = 7,
                                   "Daily" = 8),
                             label = "Frequency of Local Beer Consumption"))

expss::val_lab(NMD$freq_beer_factor)
```
##check and recode level
```{r}
expss::val_lab(NMD$good_selection_avail) #4 levels

NMD$good_select_avail_factor <- with(NMD,
                                 if_else(good_selection_avail ==1,4,
                                   if_else(good_selection_avail == 2,3,
                                     if_else(good_selection_avail ==3,2,
                                       if_else(good_selection_avail == 4,1,
                                          as.numeric(good_selection_avail)     
                                               )))))
NMD$good_select_avail_factor <- (labelled(NMD$good_select_avail_factor,
                                          c("Not Important" = 1,
                                            "Slightly Important" = 2,
                                            "Quite Important" = 3,
                                            "Very Important" = 4
                                            )))
                                            
expss::val_lab(NMD$good_select_avail_factor)

```

##set age groups

```{r}
agebreaks <- c(15, 35, 55, 75, 96)

agelabels <- c("15-35", "36-55", "56-75",
               "76-96")

setDT(NMD)[, agegroups := cut(age,
                              breaks = agebreaks,
                              right = FALSE,
                              lables = agelabels)]
expss::val_lab(NMD$agegroups)
```


```{r}
NMD %>%
  group_by(Year = Year) %>%
  summarize(gender = mean(gender),
            pay_more = mean(pay_more))

```

##see correlation and scatter plot, check for multicollinearity 

```{r, message=FALSE, warning=FALSE}
library(GGally)

ggpairs(as_factor(NMD)[,c("gender_factor",
               "age",
               "edu_level_factor",
               "pay_more_factor",
               "env_con_food_factor",
               "buy_often_factor"
)])

ggpairs(NMD[,c("pay_more_factor",
                "gender_factor",
                "age",
                "edu_level_factor",
                "env_con_food_factor",
                "buy_often_factor"
)])


ggpairs(NMD[,c("pay_more_factor",
               "freq_ost_factor",
               "freq_beer_factor"
)])


```

##change pay_more to binary by grouping Agree and Slightly Agree to 1, and Slightly disagree and Disagree to 0

```{r}

NMD$pay_more_WTP <- ifelse(
                    NMD$pay_more_factor ==1 |
                      NMD$pay_more_factor ==2, 0,
                           NMD$pay_more_factor)
NMD$pay_more_WTP <- ifelse(
                    NMD$pay_more_factor ==3 | 
                      NMD$pay_more_factor ==4, 1,
                           NMD$pay_more_WTP)
NMD$pay_more_WTP <- as_factor(NMD$pay_more_WTP)

```

##check for Missingness and go for imputation
##leave this unless Gorm has no problem with missingness

```{r, message=FALSE, warning= FALSE}
library(skimr)

skimr::skim(NMD)

```


#Summary Statistics

```{r, message = FALSE, warning=FALSE}

req <- substitute(require(x, character.only = TRUE))
libs<-c("sjPlot")
sapply(libs, function(x) eval(req) || {install.packages(x); eval(req)})
library(sjPlot)

sjPlot::tab_xtab(var.row = NMD$edu_level_factor, var.col = NMD$pay_more_factor,
                 NMD$gender_factor,
                 title = "Tabulation of Education Level and WIllingness to Pay",
                 file = "ed_pm.html", show.row.prc = TRUE)

sjPlot::tab_xtab(var.row = NMD$gender_factor, var.col = NMD$pay_more_factor,
                 title = "Tabulation of Gender and WIllingness to Pay",
                 file = "g_pm.html",
                 show.row.prc = TRUE)

sjPlot::tab_xtab(var.row = NMD$env_con_food_factor, 
                 var.col = NMD$pay_more_factor,
                 title = "Tabulation of Environmental conscious consumption habit 
                 and WIllingness to Pay", file = "env_pm.html",
                 show.row.prc = TRUE)

sjPlot::tab_xtab(var.row = NMD$freq_beer_factor, var.col = NMD$pay_more_factor,
                 title = "Tabulation of frequency of local beer consumption and WIllingness to Pay", file = "beer_pm.html",
                 show.row.prc = TRUE)

#object <- table(NMD$pay_more_factor, NMD$freq_beer_factor)
#mosaicplot(object, main = "Frequency of Beer Consumption and WTP",
 #          xlab = "X-axis label",
  #         ylab = "Y-axis label", color = TRUE)


sjPlot::tab_corr(NMD[, c("pay_more_factor", "gender_factor", "age", "buy_often_factor","env_con_food_factor", "freq_beer_factor", "freq_ost_factor", "good_select_avail_factor")], na.deletion = "listwise",
corr.method = "pearson", title = "Correlation Matrix", show.p = TRUE, digits = 2, triangle = "lower", file = "Cor_Martix.html")
```






#Logistic Regression Models

## Ordered Logistic Model 1

```{r, warning=FALSE, message=FALSE}
library(MASS)
polr_1<-polr(as_factor(pay_more_factor)~ 
                      as_factor(edu_level_factor),
                      data= NMD, Hess=TRUE
              )

summary(polr_1)

coeff_table <- coef(summary(polr_1))
coeff_table

for_se <- vcov(polr_1)

for_se

p_val <- pnorm(abs(coeff_table[, "t value"]), lower.tail = FALSE) * 2

p_val
## combined table
combinedcoeff_table <- cbind(coeff_table, "p value" = round(p_val,3))

combinedcoeff_table


library(stargazer)
stargazer(polr_1, digits = 3,
          type = "html",
          title = "Ordered Logistic Regression Table" , align = TRUE, 
          out = "OLR.html",  
          p = p_val,
          se = for_se,
          header = FALSE,
          model.numbers = FALSE,
          ord.intercepts = TRUE
          )

stargazer(for_se, type = "text", title = "VCOV", out = "vcov.txt", align = TRUE, header = FALSE)

```



## logit Model 1

```{r}
logit_1 <- glm (   pay_more_WTP ~
                              gender_factor +
                              age +
                              edu_level_factor 
                              ,
                      family = binomial (link= "logit"),
                      data = NMD)

```

```{r}
logit_1

```

## logit model 2

```{r}
logit_2 <- glm (   pay_more_WTP ~
                           gender_factor +
                           age +
                           edu_level_factor +
                           buy_often_factor,
                   family = binomial (link= "logit"),
                   data = NMD)
logit_2
```

## logit Model 3

```{r}
logit_3 <- glm (   pay_more_WTP ~
                           gender_factor +
                           age +
                           edu_level_factor +
                           buy_often_factor+
                           freq_beer_factor +
                           freq_ost_factor,
                   family = binomial (link= "logit"),
                   data = NMD)
logit_3
```

##logit Model 4

```{r}
logit_4 <- glm (   pay_more_WTP ~
                           gender_factor +
                           age +
                           edu_level_factor +
                           buy_often_factor+
                           freq_beer_factor +
                           freq_ost_factor+
                           env_con_food_factor,
                   family = binomial (link= "logit"),
                   data = NMD)
logit_4
```

##logit_moel 5

```{r}
logit_5 <- glm (   pay_more_WTP ~
                           gender_factor +
                           age +
                           edu_level_factor +
                           buy_often_factor+
                           freq_beer_factor +
                           freq_ost_factor +
                           env_con_food_factor +
                           gender_factor*edu_level_factor+
                           age*edu_level_factor,
                   family = binomial (link= "logit"),
                   data = NMD)
logit_5
```


## GLMER Model 1

```{r, warning=FALSE, message=FALSE}
library(lme4)

glmer_1 <- glmer(pay_more_WTP ~ gender_factor + edu_level_factor +
             buy_often_factor + 
             (1 | Year), data = NMD, family = binomial (link = "logit")
)

# print the mod results without correlations among fixed effects
print(glmer_1, corr = FALSE)
```

##load heteroskedasticity-robust standard errors of coefficient estimators 
in a list

```{r, warning=FALSE, message=FALSE}

library(sandwich)
for_print_se <- list(
                     sqrt(diag(vcovHC(logit_1, type = "HC1"))),
                     sqrt(diag(vcovHC(logit_2, type = "HC1"))),  
                     sqrt(diag(vcovHC(logit_3, type = "HC1"))),
                     sqrt(diag(vcovHC(logit_4, type = "HC1"))),
                     sqrt(diag(vcovHC(logit_5, type = "HC1"))))
                     
             
```

##see standard errors

```{r}
for_print_se

```

##print regression table

```{r, message=FALSE, warning=FALSE, results="asis"}

library(stargazer)
stargazer(glmer_1,logit_1, logit_2, logit_3, logit_4, logit_5, 
          digits = 3,
          type = "html",
          title = "NMD Regression Table" , align = TRUE, 
          out = "Regression_Table.html",  
          header = FALSE,
          se = for_print_se,
          model.numbers = FALSE,
          column.labels = c("(1)", "(2)","(3)", "(4)", "(5)", "(6)"))
```

```{r, message=FALSE, warining=FALSE}

library(AER)
hyp1 <- linearHypothesis(logit_5, 
                 test = "F",
                 c("edu_level_factor = 0"
                 ),
                 vcov = vcovHC, type = "HC1")
hyp2 <- linearHypothesis(logit_5, 
                 test = "F",
                 c("edu_level_factor = 0",
                   "gender_factor = 0"
                 ),
                 vcov = vcovHC, type = "HC1")

hyp3 <- linearHypothesis(logit_5, 
                 test = "F",
                 c("edu_level_factor = 0",
                   "gender_factor = 0",
                   "age = 0",
                   "buy_often_factor =0"
                 ),
                 vcov = vcovHC, type = "HC1")

hyp4 <- linearHypothesis(logit_5, 
                 test = "F",
                 c("edu_level_factor = 0",
                   "gender_factor = 0",
                   "age = 0",
                   "buy_often_factor =0",
                   "freq_beer_factor = 0",
                   "gender_factor:edu_level_factor=0",
                   "age:edu_level_factor = 0"
                 ),
                 vcov = vcovHC, type = "HC1")

stargazer(hyp1, hyp2, hyp3, hyp4,
          type = "html",
          out = "Hypothesis2.html",
          align = TRUE
          
          )

```



